STA610 Case Study 1 Team 4 Report

### 2021-03-22 STA_610_Case_Study_1_Report_Team_4.Rmd
format changed

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(pacman)
pacman::p_load(tidyverse, lme4, gridExtra, grid, ggplot2, lattice, redres, stringr, influence.ME, knitr)
# devtools::install_github("goodekat/redres")
```

@@

```{r, fig.height=2.5, fig.align='center'}
# log transform ppm
df$log_ppm <- log(df$ppm)
hist_ppm <- ggplot(df, aes(x=ppm)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white", bins = 50)+
 geom_density(alpha=.2, fill="red") 
hist_log_ppm <- ggplot(df, aes(x=log_ppm)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white", bins = 50)+
 geom_density(alpha=.2, fill="blue") 
grid.arrange(hist_ppm, hist_log_ppm, ncol=2)
```

@@

```{r, fig.align='center', fig.height = 2.5}
ggplot(df, aes(x=reorder(USA_region, USA_region, length), y=log_ppm, fill=USA_region)) +
geom_boxplot() +
labs(title="log PPM by region", x="region",y="Log PPM")
```

@@

### dose_per_mg & date_num
```{r, fig.align='center', fig.height = 2.5}
plot_dose_per_mg <- ggplot(data = df[df$state=="Florida" | df$state=="Texas" | df$state=="North Carolina",], aes(x = dose_per_mg, y = log_ppm)) + 
  geom_point() +
  facet_grid(~ state)
```

```{r, fig.align='center', fig.height = 2.5}
plot_date_num <- ggplot(data = df[df$state=="Florida" | df$state=="Texas" | df$state=="North Carolina",], aes(x = date_num, y = log_ppm)) + 
  geom_point() +
  facet_grid(~ state)

@@

```{r, fig.align='center', fig.height=8}
dotplot(ranef(mod_final, condVar=TRUE))$state
```
From the result of the random effects, we can see that the random intercept for Tennessee is the highest and it is significantly different from zero. The random intercept for Arizona is the lowest and this intercept is also significant.

>>>>

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(pacman)
pacman::p_load(tidyverse, 
               lme4, 
               gridExtra, 
               grid, 
               ggplot2, 
               lattice, 
               redres, 
               stringr, 
               influence.ME, 
               knitr, 
               merTools)
# devtools::install_github("goodekat/redres")
```

@@

```{r, fig.height=2, fig.align='center'}
# log transform ppm
df$log_ppm <- log(df$ppm)
hist_ppm <- ggplot(df, aes(x=ppm)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white", bins = 50)+
 geom_density(alpha=.2, fill="red") 
hist_log_ppm <- ggplot(df, aes(x=log_ppm)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white", bins = 50)+
 geom_density(alpha=.2, fill="blue") 
grid.arrange(hist_ppm, hist_log_ppm, ncol=2)
```

@@

```{r, fig.align='center', fig.height = 2}
ggplot(df, aes(x=reorder(USA_region, USA_region, length), y=log_ppm, fill=USA_region)) +
geom_boxplot() +
labs(title="log PPM by region", x="region",y="Log PPM")
```

@@

### dose_per_mg & date_num
```{r, fig.align='center', fig.height = 2.5, warning=FALSE, message=FALSE}
plot_dose_per_mg <- ggplot(data = df[df$state=="Florida" | df$state=="North Carolina",], aes(x = dose_per_mg, y = log_ppm)) + 
  geom_point() +
  geom_smooth(method=lm) +
  facet_grid(~ state)
```

```{r, fig.align='center', fig.height = 2.5, warning=FALSE, message=FALSE}
plot_date_num <- ggplot(data = df[df$state=="Florida" | df$state=="North Carolina",], aes(x = date_num, y = log_ppm)) + 
  geom_point() +
  geom_smooth(method=lm) +
  facet_grid(~ state)

@@

```{r, fig.align='center', fig.height=8}
dotplot(ranef(mod_final, condVar=TRUE))$state

#plotREsim(REsim(mod_final,n.sims=100),stat='median',sd=TRUE, labs = TRUE)
```
From the result of the random effects, we can see that the random intercept for Tennessee is the highest and it is significantly different from zero. The random intercept for Arizona is the lowest and this intercept is also significant.
